When are Fuzzy Extractors Possible?

### 2015-02-09 trunk/info-bounds/FuzzyExtPossibility.tex
cleaning up proof of negatie results

\begin{proof}[Proof Outline]
We prove the stronger average case statement.
Let $\nu = \omega(\log n)$ and $\nu = o(n^{1/2}/\log n)$.  Let $t=4\nu n^{1/2}$ and note that $n/\nu >t$.

@@

We now present an outline of the proof~(proofs in \apref{sec:fuzz ext proof}):
\begin{itemize}
\item \propref{prop:dist fuzzy ent fuzz}: for all $W\in \mathcal{W}$, $\Hfuzz(W) = \omega (\log n)$. That is, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
\item \propref{prop:dist uniform fuzz}: the distribution $V$ is uniform.
\item \lemref{lem:fuzz can't get key}: In expectation across $Z$, a large subset of keys that are not possible.  In more detail,
\begin{itemize}
\item Half the keys have at most $2^{n- \kappa}$ pre images in the metric space~(this is at most half the metric space).  Denote this set as $R_{small}$.  
\item Consider some $\key \in R_{small}$.  %Our goal is to show there are few values of $v \in V|Z$ that could produce this key.  
Consider the set of $V_{\key } = \{w | \rep(w, p) = \key \}$.  All points in $V | \sketch(V)$ are distance $t$ from a boundary of $V_\key$~(the functionality of $\rep$ guarantees that for the true $w$ all nearby points map to the same $\key$).  We show that most of $V_\key$ is near a boundary.  A result of Frankel and F{\"u}redi says that the boundary of a region is minimized by a ball containing the same number of points~\cite{frankl1981short}.  Hoeffding's inequality says that most of a ball lies near its boundary~\cite{hoeffding1963probability}.  Together these two results imply that $V_\key$ is small.
\item As before, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).  Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_2$ have disjoint support outside of $v$.
\item For most values of possible $Z$, the intersection between the viable pre images of $V|Z$ and $V_\key$ contains at most one point~(the received point $v$).  Checking if $V|Z \cap V_{\key}$ is nonempty is an effective distinguisher.
%The previous two propositions were similar to the secure sketch counterexample.  However, the structure on the metric space imposed byThe remainder of the proof is significantly different.  We show for any $(\gen, \rep)$ many keys have few possible values that could produce them in the metric space once $p$ is published.  Then an adversary that sees $z$ is able to eliminate many possible keys and thus effectively distinguish the key from random.
\end{itemize}
\end{itemize}

@@

%\begin{corollary}
%\label{cor:no fuzz for dist}
%Let $\mathcal{W}$ be a family of distributions.  Let $V$ be an arbitrary distribution over elements of $\mathcal{W}$.  If there does not exist a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$, then there is no $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.
%\end{corollary}
%
%Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to imperfect correctness.
\section{Fuzzy min-entropy}
\label{sec:proof fuzz necessary}
\begin{proof}[Proof of \propref{prop:fuzz necessary}]
Let $W$ be a distribution where $\Hfuzz(W) = m$.  This means that there exists a point $w' \in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, w')\leq t] = 2^{-m}$.  Consider the following distinguisher $D$:
\begin{itemize}
\item Input $r, p$.
\item If $\rep(w', p) = r$, output $1$.
\item Else output $0$.
\end{itemize}
Clearly, $\Pr[D(\Key, P) = 1]\geq 2^{-m} - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.  Thus,
\[
\sd((R, P), (U_\kappa, P)) \ge \delta^D((R, P), (U_\kappa, P))\geq 2^{-m} -\delta -2^{-\kappa}.
\]
\end{proof}
\begin{proof}[Proof of \lemref{lem:conditional fuzz rule}]
\begin{align*}
\Hfuzz(W | P=p) &= -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \Pr[W=w | P=p] \right)\\
 &= -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \frac{\Pr[W=w \wedge P=p]}{\Pr[P=p]} \right)\\
 &\ge -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \frac{\Pr[W=w]}{\Pr[P=p]} \right)\\
 &\ge -\log \left(\max_{w'}  \sum_{w\in W| \dis(w, w')\le t} \frac{\Pr[W=w]}{\Pr[P=p]} \right)\\
 &= \Hfuzz(W) + \log \Pr[P=p].
\end{align*}
\end{proof}

\begin{proof}[Proof of \lemref{lem:chain rule fuzz}]
\begin{align*}
\Hfav(W|P) &= -\log \left( \expe_{p\leftarrow P} \max_{w'} \sum_{w\in W |P =p | \dis(w, w')\le t} \Pr[W=w|P=p] \right)\\
&= -\log \left( \sum_{p} \max_{w'} \sum_{w\in W |P =p | \dis(w, w')\le t} \Pr[W=w|P=p]\Pr[P=p] \right)\\
&= -\log \left( \sum_{p} \max_{w'} \sum_{w\in W |P =p | \dis(w, w')\le t} \Pr[W=w \wedge P=p] \right)\\
&\ge -\log \left( \sum_{p} \max_{w'} \sum_{w\in W |P =p | \dis(w, w')\le t} \Pr[W=w] \right)\\
&\ge -\log \left( \sum_{p} \max_{w'} \sum_{w\in W | \dis(w, w')\le t} \Pr[W=w] \right)\\
&\ge -\log \left( 2^{H_0(P)} \left(\max_{w'} \sum_{w\in W | \dis(w, w')\le t} \Pr[W=w] \right)\right)\\
&\ge \Hfuzz(W) - H_0(P).
\end{align*}
\end{proof}

@@

\paragraph{Security:}
We now argue security of the construction.  First note that the total weight of points whose probability is less than $2^{-(n+m)}$ is at most $2^{-m}$~(there are at most $2^n$ points in the distribution).  Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-(n+m)}$.  Then 
\begin{align}
\Hav(W | \sketch(W)) &= -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\nonumber\\
&\ge -\log\left( 2^{-m} + (1-2^{-m})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\label{eq:min-entropy}\right)
\end{align}
For the remainder of the proof, we seek a bound on $\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0).$  Let $I$ be the random variable of the level information (in what follows, $I$ ranges over $m\le i \le m+n$, where possible we omit this for notational clarity).

\begin{align}
\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i\in I} 2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}}=0 \wedge I=i}) \right)\nonumber\\
&=-\log \left( \expe_{i\in I} 2^{-\Hav(W | \mathcal{K}_i \wedge F_i(K_i, W) \wedge 1_{\text{low}}=0 \wedge I=i)}\right)\nonumber\\
&=-\log \left( \expe_{i\in I} 2^{-\Hav(W |  F_i(K_i, W) \wedge 1_{\text{low}}=0 \wedge I=i)}\right)\nonumber\\
&\ge-\log \left( \expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}-1) +\log \delta)}\right)\nonumber\\
&\ge-\log \left(\frac{1}{\delta} \expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}-1))}\right)\nonumber\\
&\ge-\log \left(\expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}-1))}\right) - \log \frac{1}{\delta}\nonumber\\
&\ge-\log \left(\expe_{i\in I} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge I=i)-\log (\beta_{t, i}))}\right) - \log \frac{1}{\delta}\label{eq:fuzzy ball size}
\end{align}

\noindent
The third line follows because the only dependence between $\mathcal{K}_i$ and $W$ is in $i$.  The fourth line follows by \cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.  We now show that the fuzzy min-entropy conditioned on the level information is proportional to $\beta_{t, i}$.  
\begin{claim}
\label{cl:fuzz proportional beta}
\[\Hoo(W | 1_{\text{low}} =0 \wedge J=j ) -\log \beta_{t, i} \ge \Hfuzz(W | J=j \wedge 1_{\text{low}}=0)-1.\]
\end{claim}
\begin{proof}
For convenience denote by $J=j$ the random variable $1_{\text{low}}=0 \wedge I=i$. 
\begin{align*}
\Hfuzz(W|J=j) &= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} \Pr[W=w | J=j]\right) \right)\\
&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} \min_{w^*\in W=w| J=j}\Pr[W=w^* | J=j]\right) \right)\\
&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} \max_{w^*\in W=w| J=j}\Pr[W=w^* | J=j]\right) \right)+1\\
&= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 2^{-\Hoo(W|J=j)}\right) \right)+1\\
&= \Hoo(W|J=j)- \log\left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')} 1\right) \right)+1\\
&=\Hoo(W|J=j)-  \log \left(\max_{w' \in \mathcal{M}} \left|\{w | \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|\right)+1\\
&=\Hoo(W|J=j)+1-\log \beta_{t, i}.
\end{align*}
Where the third line follows by \clref{cl:nearly flat after conditioning}, which follow the body of the proof.  This completes the proof of \clref{cl:fuzz proportional beta}.
\end{proof}

\noindent 
We now return to the proof of \thref{thm:layered hashing}. Together Equation \ref{eq:fuzzy ball size} and \clref{cl:fuzz proportional beta} yield:
\begin{align*}
\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i\in I} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}}=0)-1}\right) -\log \frac{1}{\delta} \\
&=-\log \left( \expe_{i\in I} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}} =0)}\right) -1- \log \frac{1}{\delta} \\
&=\Hfav(W | I \wedge 1_{\text{low}}=0)-1- \log \frac{1}{\delta} \\
&\ge\Hfuzz(W | 1_{\text{low}}=0)-1-\log n -\log \frac{1}{\delta}\\
&\ge\Hfuzz(W)-1-\log n -\log \frac{1}{\delta} - \log (1-2^{-m})
\end{align*}
Where the second-to-last line follows by \lemref{lem:chain rule fuzz}.  The last line follows by \lemref{lem:conditional fuzz rule} and by noting that $\Pr[1_{\text{low}}=0] \ge 1/(1-2^{-m})$.
Returning to equation \ref{eq:min-entropy} one has:
\begin{align*}
\Hav(W | \sketch(W)) &\ge -\log\left( 2^{-m} + (1-2^{-m}) 2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\label{eq:min-entropy}\right)\\
&\ge -\log \left(2^{-m}+2^{-(\Hfuzz(W) -1 - \log n  -\log 1/\delta-2\log (1-2^{-m}) )}\right)\\
&\ge -\log \min\{2^{-m}, 2^{-(\Hfuzz(W) -1 - \log n  -\log 1/\delta-2\log (1-2^{-m}) )}\}-1\\
&\ge \Hfuzz(W) - 2- \log n - \log 1/\delta  -2\log (1-2^{-m}) \\
&\ge \Hfuzz(W) - 4- \log n - \log 1/\delta
\end{align*}
Where the fourth line follows from the third because $\Hfuzz(W)\le \Hoo(W) = m$. The last line follows from the fourth because if $m\ge 1$, then $\log (1-2^{-m}) \le 1$ and if $m<1$ the entire bound is vacuous as $\Hfuzz(W) < 1$.
\end{proof}

\begin{claim}
\label{cl:nearly flat after conditioning}
Let $W$ be a distribution and let $S\subset W$ such that for all $w_1, w_2 \in S$, $\Pr[W=w_1]\ge \Pr[W=w_2]$.  Let $J$ be as above, then for all $w_1, w_2 \in (S \wedge W|J=j )$, $\Pr[W=w_1 | J=j]\ge \Pr[W=w_2 | J=j]/2$.
\end{claim}
\begin{proof}
\begin{align*}
\Pr[W=w_1 | J=j] &=\frac{\Pr[W=w_1\wedge J=j] }{\Pr[J=j]}\\
&= \frac{\Pr[W=w_1]}{\Pr[J=j]}\\
&\ge \frac{\Pr[W=w_2]}{2 \Pr[J=j]}\\
&= \frac{\Pr[W=w_2 \wedge J=j]}{2\Pr[J=j]}\\
&=\frac{\Pr[W=w_2]}{2}.
\end{align*}
Where the first and last equality follow by Bayes' rule.  The second and fourth equality follow by noting that $\Pr[W=w \wedge J=j] = \Pr[W=w \wedge 1_{\text{low}}=0 \wedge I=i] = \Pr[W=w]$ for all $w\in L_i$.  The inequality proceeds by assumption.  This completes the proof of \clref{cl:nearly flat after conditioning}.
\end{proof}

@@

\begin{lemma}
\label{lem:fuzz can't get key}
Fix some $(\gen, \rep)$ algorithm with $\kappa \ge 2$.  There exists an information-theoretic distinguisher between $(R, P, Z)$ and $(U_\kappa, P, Z)$ with advantage $\epsilon = 1/8-\ngl(n)$.
\end{lemma}
\begin{proof}
As in the proof of \thref{thm:imposs sketch}, we assume that $\rep$ is deterministic.  Denote by $(\Key, P) \leftarrow \gen(V)$.
By Markov's inequality, there exists a set $A_{\epsilon}$ such that $\Pr[p\in A_{\epsilon}]\ge 1/2$ and $\forall p\in A_{\epsilon}$, 
\[
(\Key |P =p) \approx_{2\epsilon} (U_\kappa , P =p).
\]
%\{w' | \dis (w', w)\le t \wedge \rec(w', p) \neq w\}\le 2\delta < 1/2.\]

Consider some $p^*\in A_{p}$.  %Since $(R | P=p^*, p^*)\approx_{2\epsilon} (U, p^*)$ this means that $R|P=p^*$ is at least $(1-2\epsilon)2^\kappa$.  
The distribution $\Key|P=p^*$ is the set of possible keys.
The distribution $\Key|P=p^*$ induces a partition on the metric space.  That is, for every $w\in\mathcal{M}$, there exists a unique value $\key$ such that $\rep(w, p^*) =\key$.  Denote this partition by $Q_{p^*,\key} = \{w | \rep(w, p^*) = \key\}$.

There exists a set $R_{small}$  where $|R_{small} | \ge 2^{\kappa-1}$ such that for all $\key\in R_{small}$,  $|Q_{p^*, r}|\le \mathcal{M}/2^{\kappa} = 2^{n-\kappa }$.  If not, then $\cup_{\key} |Q_{p^*, \key}| > |\mathcal{M}|$.
For the remainder of the proof we restrict ourselves to elements in $R_{small}$.  Only points that are distance $t$ from points outside of $Q_{p^*, r}$ are viable points in the metric space.  These are the interior of $Q_{p^*, r}$: \lnote{what's $r$? in this and previous lines? also, I can parse definition of interior below}
\begin{align*}
\inter(Q_{p^*, \key}) = \{w | \rep(w, p^*) = \key \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =\key\},\\
%\crust(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\}.
\end{align*}

>>>>

\begin{proof}[Proof Outline]
We prove the stronger average case statement.
Let $\nu = \omega(\log n)$ and $\nu = o(n^{1/2}/\log n)$.  Let $t=4\nu n^{1/2}+1$ and note that $n/\nu >t$.

@@

We now present an outline of the proof~(proofs in \apref{sec:fuzz ext proof}):
\begin{itemize}
\item \propref{prop:dist fuzzy ent fuzz}: for all $W\in \mathcal{W}$, $\Hfuzz(W) = \omega (\log n)$. That is, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
\item \propref{prop:dist uniform fuzz}: the distribution $V$ is uniform.
\item \lemref{lem:fuzz can't get key}: In expectation across $Z$, a large subset of keys that are not possible.  In more detail,
\begin{itemize}
\item Half the keys have at most $2^{n- \kappa}$ pre images in the metric space~(this is at most half the metric space).  Denote this set as $\Key_{small}$.  
\item Consider some $\key \in \Key_{small}$.  %Our goal is to show there are few values of $v \in V|Z$ that could produce this key.  
Consider the set of $V_{\key } = \{w | \rep(w, p) = \key \}$.  All points in $V | \sketch(V)$ are distance $t$ from a boundary of $V_\key$~(the functionality of $\rep$ guarantees that for the true $w$ all nearby points map to the same $\key$).  We show that most of $V_\key$ is near a boundary.  A result of Frankel and F{\"u}redi says that the boundary of a region is minimized by a ball containing the same number of points~\cite{frankl1981short}.  Hoeffding's inequality says that most of a ball lies near its boundary~\cite{hoeffding1963probability}.  Together these two results imply that $V_\key$ is small.
\item As before, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).  Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_2$ have disjoint support outside of $v$.
\item For most values of possible $Z$, the intersection between the viable pre images of $V|Z$ and $V_\key$ contains at most one point~(the received point $v$).  Checking if $V|Z \cap V_{\key}$ is nonempty is an effective distinguisher.
%The previous two propositions were similar to the secure sketch counterexample.  However, the structure on the metric space imposed byThe remainder of the proof is significantly different.  We show for any $(\gen, \rep)$ many keys have few possible values that could produce them in the metric space once $p$ is published.  Then an adversary that sees $z$ is able to eliminate many possible keys and thus effectively distinguish the key from random.
\end{itemize}
\end{itemize}

@@

%\begin{corollary}
%\label{cor:no fuzz for dist}
%Let $\mathcal{W}$ be a family of distributions.  Let $V$ be an arbitrary distribution over elements of $\mathcal{W}$.  If there does not exist a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$, then there is no $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.
%\end{corollary}
%
%Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to imperfect correctness.
\section{Fuzzy min-entropy}
\label{sec:proof fuzz necessary}
In this section, we provide proofs of the items in \secref{sec:minimal conditions}.  
\begin{proof}[Proof of \propref{prop:fuzz necessary}]
Let $W$ be a distribution where $\Hfuzz(W) = m$.  This means that there exists a point $w' \in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, w')\leq t] = 2^{-m}$.  Consider the following distinguisher $D$:
\begin{itemize}
\item Input $\key, p$.
\item If $\rep(w', p) = \key$, output $1$.
\item Else output $0$.
\end{itemize}
Clearly, $\Pr[D(\Key, P) = 1]\geq 2^{-m} - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.  Thus,
\[
\sd((\Key, P), (U_\kappa, P)) \ge \delta^D((\Key, P), (U_\kappa, P))\geq 2^{-m} -\delta -2^{-\kappa}.
\]
This completes the proof of \propref{prop:fuzz necessary}.
\end{proof}
\begin{proof}[Proof of \lemref{lem:conditional fuzz rule}]
\begin{align*}
\Hfuzz(W | P=p) &= -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \Pr[W=w | P=p] \right)\\
 &= -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \frac{\Pr[W=w \wedge P=p]}{\Pr[P=p]} \right)\\
% &\ge -\log \left(\max_{w'}  \sum_{w\in (W |P=p) | \dis(w, w')\le t} \frac{\Pr[W=w]}{\Pr[P=p]} \right)\\
 &\ge -\log \left(\max_{w'}  \sum_{w\in W| \dis(w, w')\le t} \frac{\Pr[W=w]}{\Pr[P=p]} \right)\\
 &= \Hfuzz(W) + \log \Pr[P=p].
\end{align*}
This completes the proof of \lemref{lem:conditional fuzz rule}.
\end{proof}

\begin{proof}[Proof of \lemref{lem:chain rule fuzz}]
\begin{align*}
\Hfav(W|P) &= -\log \left( \expe_{p\leftarrow P} \max_{w'} \sum_{w\in W |P =p | \dis(w, w')\le t} \Pr[W=w|P=p] \right)\\
&= -\log \left( \sum_{p} \max_{w'} \sum_{w\in W |P =p | \dis(w, w')\le t} \Pr[W=w|P=p]\Pr[P=p] \right)\\
&= -\log \left( \sum_{p} \max_{w'} \sum_{w\in W |P =p | \dis(w, w')\le t} \Pr[W=w \wedge P=p] \right)\\
&\ge -\log \left( \sum_{p} \max_{w'} \sum_{w\in W |P =p | \dis(w, w')\le t} \Pr[W=w] \right)\\
&\ge -\log \left( \sum_{p} \max_{w'} \sum_{w\in W | \dis(w, w')\le t} \Pr[W=w] \right)\\
&\ge -\log \left( 2^{H_0(P)} \left(\max_{w'} \sum_{w\in W | \dis(w, w')\le t} \Pr[W=w] \right)\right)\\
&\ge \Hfuzz(W) - H_0(P).
\end{align*}
This completes the proof of \lemref{lem:chain rule fuzz}.
\end{proof}

@@

\paragraph{Security:}
We now argue security of the construction.  First note that the total weight of points whose probability is less than $2^{-(n+m)}$ is at most $2^{-m}$~(there are at most $2^n$ points in the distribution).  Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-(n+m)}$.  Then 
\begin{align}
\Hav(W | \sketch(W)) &= -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\nonumber\\
&\ge -\log\left( 2^{-m} + (1-2^{-m})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\label{eq:min-entropy}\right)
\end{align}
For the remainder of the proof, we seek a bound on $\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0).$  Let $L_I$ be the random variable of the level information (in what follows, $L_I$ takes values between $m$ and $m+n$, where possible we omit this for notational clarity).

\begin{align}
\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i} 2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}}=0 \wedge L_I =i }) \right)\nonumber\\
&=-\log \left( \expe_{i} 2^{-\Hav(W | \mathcal{K}_i \wedge F_i(K_i, W) \wedge 1_{\text{low}}=0 \wedge L_I=i)}\right)\nonumber\\
&=-\log \left( \expe_{i} 2^{-\Hav(W |  F_i(K_i, W) \wedge 1_{\text{low}}=0 \wedge L_I=i)}\right)\nonumber\\
&\ge-\log \left( \expe_{i} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge L_I=i)-\log (\beta_{t, i}-1) +\log \delta)}\right)\nonumber\\
&\ge-\log \left(\frac{1}{\delta} \expe_{i} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge L_I=i)-\log (\beta_{t, i}-1))}\right)\nonumber\\
&\ge-\log \left(\expe_{i} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge L_I=i)-\log (\beta_{t, i}-1))}\right) - \log \frac{1}{\delta}\nonumber\\
&\ge-\log \left(\expe_{i} 2^{-(\Hav(W |  1_{\text{low}}=0 \wedge L_I=i)-\log (\beta_{t, i}))}\right) - \log \frac{1}{\delta}\label{eq:fuzzy ball size}
\end{align}

\noindent
The third line follows because the only dependence between $\mathcal{K}_i$ and $W$ is in $i$.  The fourth line follows by \cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.  We now show that the fuzzy min-entropy conditioned on the level information is proportional to $\beta_{t, i}$.  For convenience denote by $J \overset{def}= (L_I \wedge 1_{\text{low}}=0)$.  That is, $\Pr[J=i] \overset{def}= \Pr[1_{\text{low}}=0 \wedge L_I=i$]. 
\begin{claim}
\label{cl:fuzz proportional beta}
$\Hoo(W |   J=i ) -\log \beta_{t, i} \ge \Hfuzz(W | J=i)-1.$
\end{claim}
\begin{proof}
\begin{align*}
\Hfuzz(W|J=i) &= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t} \Pr[W=w | J=i]\right) \right)\\
&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t}\left( \min_{w^*\in W=w| J=i}\Pr[W=w^* | J=i]\right) \right)\right)\\
&\le -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t} \left(\max_{w^*\in W=w| J=i}\Pr[W=w^* | J=i]\right) \right)\right)+1\\
&= -\log \left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t} 2^{-\Hoo(W|J=i)}\right) \right)+1\\
&= \Hoo(W|J=i)- \log\left(\max_{w' \in \mathcal{M}} \left( \sum_{w\in W | \Pr[W=w]\in L_i \wedge \dis(w, w')\le t} 1\right) \right)+1\\
&=\Hoo(W|J=i)-  \log \left(\max_{w' \in \mathcal{M}} \left|\{w | \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|\right)+1\\
&=\Hoo(W|J=i)+1-\log \beta_{t, i}.
\end{align*}
Where the third line follows by \lemref{lem:nearly flat after conditioning}, which follows the proof of \thref{thm:layered hashing}.  This completes the proof of \clref{cl:fuzz proportional beta}.
\end{proof}

\noindent 
We now return to the proof of \thref{thm:layered hashing}. Together Equation \ref{eq:fuzzy ball size} and \clref{cl:fuzz proportional beta} yield:
\begin{align*}
\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &=-\log \left( \expe_{i} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}}=0)-1}\right) -\log \frac{1}{\delta} \\
&=-\log \left( \expe_{i} 2^{-\Hfuzz(W | I=i \wedge 1_{\text{low}} =0)}\right) -1- \log \frac{1}{\delta} \\
&=\Hfav(W | I \wedge 1_{\text{low}}=0)-1- \log \frac{1}{\delta} \\
&\ge\Hfuzz(W | 1_{\text{low}}=0)-1-\log n -\log \frac{1}{\delta}\\
&\ge\Hfuzz(W)-1-\log n -\log \frac{1}{\delta} - \log (1-2^{-m})
\end{align*}
Where the second-to-last line follows by \lemref{lem:chain rule fuzz}.  The last line follows by \lemref{lem:conditional fuzz rule} and by noting that $\Pr[1_{\text{low}}=0] \ge 1/(1-2^{-m})$.
Returning to equation \ref{eq:min-entropy} one has:
\begin{align*}
\Hav(W | \sketch(W)) &\ge -\log\left( 2^{-m} + (1-2^{-m}) 2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\label{eq:min-entropy}\right)\\
&\ge -\log \left(2^{-m}+2^{-(\Hfuzz(W) -1 - \log n  -\log 1/\delta-2\log (1-2^{-m}) )}\right)\\
&\ge -\log \min\{2^{-m}, 2^{-(\Hfuzz(W) -1 - \log n  -\log 1/\delta-2\log (1-2^{-m}) )}\}-1\\
&\ge \Hfuzz(W) - 2- \log n - \log 1/\delta  -2\log (1-2^{-m}) \\
&\ge \Hfuzz(W) - 4- \log n - \log 1/\delta
\end{align*}
Where the fourth line follows from the third because $\Hfuzz(W)\le \Hoo(W) = m$. The last line follows from the fourth because if $m\ge 1$, then $\log (1-2^{-m}) \le 1$ and if $m<1$ the entire bound is vacuous as $\Hfuzz(W) < 1$.
\end{proof}

\begin{lemma}
\label{lem:nearly flat after conditioning}
Let $W$ be a distribution and let $S\subset W$ such that for all $w_1, w_2 \in S$, $\Pr[W=w_1]\ge \Pr[W=w_2]$.  Let $J$ be as above, then for all $w_1, w_2 \in (S \wedge W|J=j )$, $\Pr[W=w_1 | J=j]\ge \Pr[W=w_2 | J=j]/2$.
\end{lemma}
\begin{proof}
\begin{align*}
\Pr[W=w_1 | J=j] &=\frac{\Pr[W=w_1\wedge J=j] }{\Pr[J=j]}\\
&= \frac{\Pr[W=w_1]}{\Pr[J=j]}\\
&\ge \frac{\Pr[W=w_2]}{2 \Pr[J=j]}\\
&= \frac{\Pr[W=w_2 \wedge J=j]}{2\Pr[J=j]}\\
&=\frac{\Pr[W=w_2 | J=j]}{2}.
\end{align*}
Where the first and last equality follow by Bayes' rule.  The second and fourth equality follow by noting that $\Pr[W=w \wedge J=j] = \Pr[W=w \wedge 1_{\text{low}}=0 \wedge I=i] = \Pr[W=w]$ for all $w\in L_i$.  The inequality proceeds by assumption.  This completes the proof of \lemref{lem:nearly flat after conditioning}.
\end{proof}

@@

\begin{lemma}
\label{lem:fuzz can't get key}
Fix some $(\gen, \rep)$ algorithm with $\kappa \ge 2$.  There exists an information-theoretic distinguisher between $(\Key, P, Z)$ and $(U_\kappa, P, Z)$ with advantage $\epsilon = 1/8-\ngl(n)$.
\end{lemma}
\begin{proof}
As in the proof of \thref{thm:imposs sketch}, we assume that $\rep$ is deterministic.  Denote by $(\Key, P) \leftarrow \gen(V)$.
By Markov's inequality, there exists a set $A_{\epsilon}$ such that $\Pr[p\in A_{\epsilon}]\ge 1/2$ and $\forall p\in A_{\epsilon}$, 
\[
(\Key |P =p) \approx_{2\epsilon} (U_\kappa , P =p).
\]
%\{w' | \dis (w', w)\le t \wedge \rec(w', p) \neq w\}\le 2\delta < 1/2.\]

Consider some $p^*\in A_{p}$.  
The distribution $\Key|P=p^*$ is the set of possible keys.
The distribution $\Key|P=p^*$ induces a partition on the metric space.  That is, for every $w\in\mathcal{M}$, there exists a unique value $\key$ such that $\rep(w, p^*) =\key$.  Denote this partition by $Q_{p^*,\key} = \{w | \rep(w, p^*) = \key\}$.

There exists a set $\Key_{small}$  where $|\Key_{small} | \ge 2^{\kappa-1}$ such that for all $\key\in \Key_{small}$,  $|Q_{p^*, \key}|\le \mathcal{M}/2^{\kappa} = 2^{n-\kappa }$.  If not, then $\cup_{\key} |Q_{p^*, \key}| > |\mathcal{M}|$.
For the remainder of the proof we restrict ourselves to elements in $\Key_{small}$.  Only points that are distance $t$ from points outside of $Q_{p^*, r}$ are viable points in the metric space.  These are points where all points within distance $t$ map to the same key.  We call this set the interior of $Q_{p^*, \key}$: 
\begin{align*}
\inter(Q_{p^*, \key}) = \{w | \rep(w, p^*) = \key \wedge (\forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =\key)\},\\
%\crust(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\}.
\end{align*}
 The isoperimetric inequality says $\inter(Q_{p^*, \key})$ must be of bounded size.  This statement use the sets which are nearly balls in the Hamming space\footnote{In most statements of the isoperimetric inequality, this type of set is simply called a ball.  We use the term near ball for emphasis.}:
\begin{definition}
A set $S$ is a $\eta$-near ball if there exists a point $x$ such that $B_{\eta-1}(x) \subseteq S \subseteq B_{\eta}(x)$.
\end{definition}
\noindent
We now show for any $\key^*$, $\inter(Q_{p^*, \key^*})$ is small:
